---
title: "Statistical analysis"
author: "ankitak"
date: "10/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## Loading Libraries

```{r DataLoading}

library("data.table")
library("ggplot2")
```

## Task

```{r Stuff}
# set seed for reproducability
set.seed(31)
# set lambda to 0.2
lambda <- 0.2

n <- 40

simulations <- 1000

simulated_exponentials <- replicate(simulations, rexp(n, lambda))
# mean of exponentials
means_exponentials <- apply(simulated_exponentials, 2, mean)
```

## part 1
To show where the distribution is centered at and compare it to the theoretical center of the distribution.

```{r}
analytical_mean <- mean(means_exponentials)
analytical_mean
```

```{r}
# analytical mean
theory_mean <- 1/lambda
theory_mean
```

```{r}

hist(means_exponentials, xlab = "mean",main = "Exponential function Simulation")
abline(v = analytical_mean, col = "orange")
abline(v = theory_mean, col = "blue")
```

The analytics mean is 4.993867 the theoretical mean 5. The center of distribution of averages of 40 exponentials is very close to the theoretical center of the distribution.

## part 2

To show what variable it is and compare it to the theoretical variance of the distribution.. 

```{r}
# standard deviation of distribution
standard_deviation_dist <- sd(means_exponentials)
standard_deviation_dist
```

```{r}
# standard deviation from analytical expression
standard_deviation_theory <- (1/lambda)/sqrt(n)
standard_deviation_theory
```

```{r}
# variance of distribution
variance_dist <- standard_deviation_dist^2
variance_dist
```

```{r}
# variance from analytical expression
variance_theory <- ((1/lambda)*(1/sqrt(n)))^2
variance_theory
```


## part 3
To show that the distribution is approximately normal.

```{r}
xfit <- seq(min(means_exponentials), max(means_exponentials), length=100)
yfit <- dnorm(xfit, mean=1/lambda, sd=(1/lambda/sqrt(n)))
hist(means_exponentials,breaks=n,prob=T,col="blue",xlab = "mean",main="Density of mean",ylab="density")
lines(xfit, yfit,pch=22,col="black",lty=5)
```

```{r}
# compare the distribution of averages of 40 exponentials to a normal distribution
 qqnorm(means_exponentials)
qqline(means_exponentials, col = 2)
```

